---
output:
  html_document:
    css: css/style.css
---

<style type="text/css">
h4 {
  font-size: 20px;
  font-weight: bold;
}

</style>

```{r include = FALSE}
source("markdown/includeRd.r")
source("markdown/includeRmd.r")
```

<div class = "container">
<div class="tabs">
  <input id="tab-1" type="radio" name="radio-set" class="tab-selector-1" checked="checked" />
  <label for="tab-1" class="tab-label-1">Genostats</label>

  <input id="tab-2" type="radio" name="radio-set" class="tab-selector-2" />
  <label for="tab-2" class="tab-label-2">Hervé Perdry</label>

<!--
<input id="tab-3" type="radio" name="radio-set" class="tab-selector-3" />
<label for="tab-3" class="tab-label-3">References</label>

<input id="tab-4" type="radio" name="radio-set" class="tab-selector-4" />
<label for="tab-4" class="tab-label-4">Contact us</label>
-->       

<div class="clear-shadow"></div>
			

<!--
<div class="side-content">

<div class="side-content-1">
<ul>
<li> Blah </li>
<li> Blah Blah Blah Blah </li>
<li> Bluh Bluh Bluh Bluh </li>
</ul>
</div>

</div>
-->

<div class="content">
<div class="content-1">

## Genostats

We develop software (R packages) and methods for genetic data analysis.

* Gaston is an R package for Genetic data analysis : data manipulation (quality control), computation of GRM, heritability estimates, association testing.

* Fantasio is an R package for homozygosity mapping with dense SNP data (beta version)

* Ravages is an R package for the analysis of rare variants (beta version)


<span style = "color:red; font-size:100%"> This site is under construction </span>

</div>

<div class="content-2">
## Hervé Perdry

```{r echo = FALSE, results = "asis"}
includeRmd("herve.perdry.Rmd", strip.level = 1, level.shift = 2)
```
</div>

<!--
<div class="content-3">
           <p>Some content</p>
</div>

<div class="content-4">
           <p>Some content</p>
</div>
-->
</div>

</div>
</div>
